@node Xtensa
@chapter Functions for Xtensa Processors

This chapter describes machine-dependent functions that are included
in the C library when it is built for Xtensa processors.

@menu
* setjmp::      Save stack environment
* longjmp::     Non-local goto
@end menu

@page
@node setjmp
@section @code{setjmp}---save stack environment
@findex setjmp
@strong{Synopsis}
@example
#include <setjmp.h>
int setjmp(jmp_buf env);

@end example
@strong{Description}@*
@code{setjmp} and @code{longjmp} are useful for dealing with errors
and interrupts encountered in a low-level subroutine of a program.
@code{setjmp} saves the stack context/environment in @code{env} for
later use by @code{longjmp}.  The stack context will be invalidated if
the function which called @code{setjmp} returns.

@*
@strong{Returns}@*
@code{setjmp} returns 0 if returning directly, and non-zero when
returning from @code{longjmp} using the saved context.

@*
@strong{Portability}@*
@code{setjmp} is ANSI C and POSIX.1.

setjmp requires no supporting OS subroutines.

@*
@page
@node longjmp
@section @code{longjmp}---non-local goto
@findex longjmp
@strong{Synopsis}
@example
#include <setjmp.h>
void longjmp(jmp_buf env, int val);

@end example
@strong{Description}@*
@code{longjmp} and @code{setjmp} are useful for dealing with errors
and interrupts encountered in a low-level subroutine of a program.
@code{longjmp} restores the environment saved by the last call of
@code{setjmp} with the corresponding @code{env} argument.  After
@code{longjmp} is completed, program execution continues as if the
corresponding call of @code{setjmp} had just returned the value
@code{val}.  @code{longjmp} cannot cause 0 to be returned.  If
@code{longjmp} is invoked with a second argument of 0, 1 will be
returned instead.

@*
@strong{Returns}@*
This function never returns.

@*
@strong{Portability}@*
@code{longjmp} is ANSI C and POSIX.1.

longjmp requires no supporting OS subroutines.

@*
